\documentclass{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\theoremstyle{definition}
\newtheorem{thm}{Theorem}
\newtheorem{axiom}{Axiom}
\renewcommand{\qedsymbol}{Q.E.D.}
\title{Reasons for Using Haskell}
\author{Varik Valefor}
\begin{document}
	\maketitle
	\section{Definitions}
		\[
			h := \textrm{Haskell}.
		\]
		Where $l$ denotes an arbitrary programming language,
		\[
			A := \left\{l: \textrm{VARIK HAS USED } l\right\} - h.
		\]
	\section{Arguments}
	\begin{axiom}[The Fundamental Rule of Language Superiority]
		For all programming languages $a$, for all programming languages $b$, $a$ is superior to $b$ if each following condition is met:
		\begin{itemize}
			\item The readability of $a$ source code is greater than the readability of $b$ source code.
			\item The ease of writing $a$ source code is greater than the ease of writing $b$ source code.
			\item The efficiency of $a$'s best compiler is greater than or approximately equal to the efficiency of $b$'s best compiler.
			\item The ease of searching for security vulnerabilities in $a$ programs is greater than the ease of searching for security vulnerabilities in $b$ programs.
			\item The documentation of $a$ is superior to the documentation of $b$.
			\item The ease of maintaining $a$ programs is greater than the ease of maintaining $b$ programs.
		\end{itemize}
	\end{axiom}
	\begin{axiom}
		For all $a \in A$, the ease of reading $h$ source code is greater than
		the ease of reading $a$ source code.
	\end{axiom}
	\begin{axiom}
		For all $a \in A$, the ease of writing $h$ source code is greater than
		the ease of reading $a$ source code.
	\end{axiom}
	\begin{axiom}
		For all $a \in A$, the efficiency of the best $a$ compiler is less than
		or approximately equal to the efficiency of the best $h$ compiler.
	\end{axiom}
	\begin{thm}
		For all $a \in A$, the ease of searching for
		security vulnerabilities in $h$ programs is greater than the
		ease of searching for security vulnerabilities in $a$ programs.
	\end{thm}
	\begin{proof}
		For all $a \in A$, the ease of reading $a$ source code is
		less than the ease of reading $h$ source code.

		For any computer program $p$ which is written in a programming language
		$l$, the ease of searching for security vulnerabilities in $p$ is
		proportional to the ease of reading $l$ source code.

		Therefore, for all $a \in A$, the ease of searching for security
		vulnerabilities in $h$ programs is greater than the ease of searching
		for security vulnerabilities in $a$ programs.
	\end{proof}
	\begin{thm}
		For all $a \in A$, the documentation of $h$ is superior to the
		documentation of $a$.
	\end{thm}
	\begin{proof}
		Assume that for all programming languages $a$, for all programming
		languages $b$, $a$'s documentation is superior to $b$'s documentation
		if there exists a well-written, mathematics-based specification of $a$
		and there does not exist a well-written, mathematics-based
		specification of $b$.

		There exists a well-written, mathematics-based specification of $h$.

		For all $a \in A$, there does not exist a well-written,
		mathematics-based specification of $a$.

		Therefore, for all $a \in A$, the documentation of $h$ is superior to
		the documentation of $a$.
	\end{proof}
	\begin{thm}
		%For all $a \in A$, the ease of maintaining $h$ programs is greater than
		%the ease of maintaining $a$ programs.
		$\forall a \in A, \ x(h) > x(a)$, where for all programming languages
		$a$, $x(a)$ denotes the ease of maintaining $a$ programs.
	\end{thm}
	\begin{proof}
		For all computer programming languages $a$, let $w(a)$ denote the ease
		of writing $a$ programs, let $r(a)$ denote the ease of reading $a$
		programs, and let $x(a)$ denote the ease of maintaining $a$ programs.

		For all programming languages $a$, for all programming languages $b$,
		\[
			x(a) > x(b) \iff \Big(r(a) > r(b)\Big) \land \Big(w(a) > w(b)\Big).
		\]

		\[
			\forall a \in A, \ r(h) > r(a).
		\]

		\[
			\forall a \in A, \ w(h) > w(a).
		\]

		\[
			\therefore \forall a \in A, \ x(h) > x(a).
		\]
	\end{proof}
\end{document}
